\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T5]{fontenc} 
\usepackage{geometry}
\geometry{a4paper, margin=0.75in} 
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=black,
}

\titleformat{\section}{\Large\bfseries\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1ex}

\pagestyle{empty}

\begin{document}

% --- THÔNG TIN LIÊN HỆ ---
\begin{center}
    \textbf{\Large LAM DUC CUONG} \\
    \href{mailto:lamcuongghj@gmail.com}{lamcuongghj@gmail.com} \textbar \ 0342322899 \textbar \ GitHub: \href{https://github.com/CuongLam1206}{CuongLam1206}
\end{center}

% --- SUMMARY QUY CHUẨN JD VIBE CODER (MỚI THÊM) ---
\section*{SUMMARY}
\noindent Tech-savvy Junior Developer with a strong \textbf{AI-first mindset} and proven ability to build software quickly leveraging AI coding tools (Claude, Cursor, Antigravity). Experienced in developing full-stack applications and AI integrations with a focus on rapid execution, problem-solving, and continuous learning.

% --- HỌC VẤN ---
\section*{EDUCATION}
\noindent\textbf{Hanoi University of Industry (HaUI)} \hfill 2023 -- Present \\
Bachelor of Electronics and Telecommunications (Year 3) \\
\textbf{GPA: 3.22/4.0}

% --- KINH NGHIỆM ---
\section*{EXPERIENCE}
\noindent\textbf{HaUI University Informatics Olympic Team} \hfill 2023 -- Present \\
Team member representing Hanoi University of Industry in competitive programming competitions. Strong algorithmic foundation aiding in extremely fast AI-assisted feature verification.

% --- HOẠT ĐỘNG ---
\section*{ACTIVITIES}
\noindent\textbf{Teaching Assistant at HIT Informatics Club} \hfill 2023 -- Present \\
Instructor for Python Basic, and AI/ML course. Regularly upskilling students on modern development workflows.

% --- KỸ NĂNG CHUYÊN MÔN ---
\section*{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{AI-Assisted Development:} Cursor, GitHub Copilot, Claude 3.5+, Antigravity agent. Strong in Prompt Engineering, AI architecture planning, and rapid prototyping.
    \item \textbf{Programming Languages:} Python (Advanced), TypeScript/JavaScript (React basics), C/C++.
    \item \textbf{Backend \& Architecture:} FastAPI, Node.js basics, Modular Architecture, Async I/O, REST APIs.
    \item \textbf{Databases \& Systems:} MongoDB, ChromaDB (Vector DB), Git/GitHub, Linux, Docker.
    \item \textbf{AI Integrations (Building Features):} RAG Pipelines, Concept of LLM APIs (Gemini, OpenRouter, Groq).
\end{itemize}

% --- DỰ ÁN ---
\section*{PROJECTS}
\noindent\textbf{Chatbot for Student Queries on HaUI Training Rules} \hfill \href{https://github.com/CuongLam1206/Chatbox_Haui}{GitHub}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt]
    \item \textbf{Rapidly developed} a production-ready Agentic RAG chatbot, heavily utilizing AI-assisted coding tools to accelerate the delivery of complex features.
    \item Designed a modular, procedural pipeline (Router $\to$ Rewriter $\to$ Retriever $\to$ Grader $\to$ Generator) minimizing overhead without relying on bloated state-graph frameworks.
    \item Built an asynchronous FastAPI backend acting as a Facebook Messenger webhook, capable of resolving heavy concurrent traffic utilizing ThreadPool and Semaphore.
    \item Integrated multi-model fallbacks (Gemini, Ollama, Groq) to optimize performance, alongside a robust hybrid search pipeline (ChromaDB + BM25).
\end{itemize}
\emph{Technical Skills: AI-Assisted Coding, Python, FastAPI, Async I/O, Hybrid RAG, Prompt Engineering, MongoDB}

\vspace{0.5em}

\noindent\textbf{Text-to-Image Generation System with LoRA Fine-Tuning} \hfill \href{https://github.com/AE-AI-HIT15/HIT_LungTung}{GitHub}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt]
    \item Developed a full-stack text-to-image application with a lightweight HTML/JS frontend and decoupled backend.
    \item Utilized Claude/Copilot to efficiently construct event-driven APIs, implement caching strategies, and handle complex data pipelines.
    \item Implemented Vietnamese $\to$ English prompt translation logic to increase application usability.
\end{itemize}
\emph{Technical Skills: Full-stack Prototyping, HTML/JS, FastAPI, Diffusion Models APIs, Modular Architecture}

% --- THÀNH TÍCH & CHỨNG CHỈ ---
\section*{ACHIEVEMENTS \& CERTIFICATIONS}
\noindent\textbf{3rd Prize} - Informatics Olympiad -- National Level \hfill Dec 2023 \\
\noindent\textbf{4th Prize} - Scientific Research Competition -- University Level \hfill May 2025 \\
\noindent\textbf{1st Prize} - Final Project, HIT Product (HIT CLUB) \hfill Aug 2025 \\
\noindent\textbf{2nd Prize} - "AI Assistant" Application Development Competition \textbf{(2/20)} -- University Level \hfill Dec 2025

\end{document}
